---
title: "Self-assessment experiment data analysis"
author: "Carlos Granell"
data: "15/04/2020 updated(`r format(Sys.time(), '%d %B, %Y')`)"
output: html_notebook
---


This document analyses the pre- and post- (soon) questionnaires as part of the experiment **Reproducibility of GIScience MSc Theses - Self-assessment experiment** - see [OSF project](https://osf.io/j97zp/)


## Reproduce paper

To create the PDF of the computational notebook you can run the following commands in a new R session.
If you have problems rendering the PDF you can execute each chunk independently in [RStudio](https://rstudio.com/products/rstudio/).

```{r render_with_rmarkdown, eval=FALSE}
require("knitr")
require("rmarkdown")
rmarkdown::render("self-assessment-experiment.Rmd", output_format = "pdf_document")
```

## Software dependencies and code

This document does not install the required R packages by default.
You can run the script `install.R` to install all required dependencies on a new R installation, or use `install.packages(..)` to install missing R packages.

```{r install_r, eval=FALSE}
source("install.R")
```

The plots and tables of survey data and evaluation use the packages [`ggplot2`](http://ggplot2.tidyverse.org/), [`knitr::kable()`](https://yihui.name/knitr/), [`huxtable`](https://hughjonesd.github.io/huxtable/), and [`kableExtra`](https://cran.r-project.org/package=kableExtra).
Required libraries and runtime environment description are as follows.

```{r load_libraries, echo=TRUE, message=FALSE, warning=FALSE}
library("tidyverse")
# library("readr")
# library("ggplot2")
# library("reshape2")
# library("ggthemes")
# library("grid")
# library("gridBase")
# library("gridExtra")
# library("kableExtra")
# library("huxtable")
library("here")
library("googlesheets4")
```

```{r set_seed}
# just in case
set.seed(nchar("Self-assessment experiment"))
```


## Download raw survey data


## Reproduciblity assessment

```{r pretestdata_file}
pretest_file <- here::here("data-raw", "pre-test.csv")
```

```{r pretestdata_download, echo=FALSE, eval=FALSE}


retest_url <- ""

pretest_sheet <- read_sheet("https://drive.google.com/open?id=1YhcOeTg04AXh7mbDzjqefuuHUG91sr98e15rl92M2Zk")


pretest_sheet <- 
  pretest_sheet %>%
  filter(`Please choose your MASTER programme` %in% c("MSc in Geospatial Technologies (UJI, NOVA IMS, IFGI-WWU)",
                                                      "MSc Geomatics Master (TU Delft)"))

write.csv(petest_sheet, file = pretest_file, append = FALSE)

```

The following plots are based on the file `r pretest_file`, filtered to _MSc in Geospatial Technologies (UJI, NOVA IMS, IFGI-WWU)_ and _MSc Geomatics (TU Delft)_.

```{r load_evaldata,warning=FALSE}

```


